Eco-evolutionary dynamics of finite populations from first principles

### 2023-02-27 ind_files/03_BD_processes.tex
Make figure legends consistent

\myfig{0.9}{Media/3.2_BD_process_2D.png}{\textbf{(A)} Consider a population of birds in which individuals are either red or blue. In this case, we have $m=2$, since there are two types of individuals in the population. \textbf{(B)} The state of the system can be described by a vector containing the number of individuals of each discrete type (in this case, the number of red and blue birds in the population). Births and deaths result in changes in the elements of the state vector.}{fig_nD_pop_description}

>>>>

\myfig{0.9}{Media/3.2_BD_process_2D.png}{\textbf{Schematic description of a one-dimensional birth-death process}. \textbf{(A)} Consider a population of birds in which individuals are either red or blue. In this case, we have $m=2$, since there are two types of individuals in the population. \textbf{(B)} The state of the system can be described by a vector containing the number of individuals of each discrete type (in this case, the number of red and blue birds in the population). Births and deaths result in changes in the elements of the state vector.}{fig_nD_pop_description}
